Structured Versus Decorated Cospans

### 2020-11-21 cospans.tex
work on Petri net section

Each set of species $S$ gives rise to a discrete Petri net $L(S)$ with $S$ as its set of species and no transitions. Master and the first author show the existence of a left adjoint $L \maps \Set \to \Petri$ where $\Petri$ is the category whose objects are Petri nets and whose `morphisms are morphisms of Petri nets'. They also show that $\Petri$ has finite colimits and thus using Theorem \cref{thm:SC} obtain a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets which has:
\item{horizontal 1-cells as open Petri nets which are given by cospans in $\Petri$ of the form:

@@

(D) edge node [above] {$I$} (E)
(F) edge node [above] {$O$} (E);
\item{2-morphisms as maps of cospans in $\Petri$ of the form:

@@

\node (F') at (5,-1) {$L(Y_2)$};

>>>>

There is a category $\Petri$ with Petri nets as objects, where a morphism from the Petri net 
$s, t \maps T \to \N[S]$ to the Petri net $s', t' \maps T' \to \N[S']$ is a pair of functions $f \maps T \to T', g \maps S \to S'$ such that the following diagrams commute:
	\xymatrix{ 
		T \ar[d]_f  \ar[r]^-{s} & \N[S] \ar[d]^-{\N[g]} \\	
		T' \ar[r]^-{s'} & \N[S'] 
	\qquad
	\xymatrix{ 
		T \ar[d]_f  \ar[r]^-{t} & \N[S] \ar[d]^-{\N[g]} \\	
		T' \ar[r]^-{t'} & \N[S'] . 
There is a functor $R \maps \Petri \to \Set$ sending any Petri net to its set of places, and this has
a left adjoint $L \maps \Set \to \Petri$ sending any set $S$ to the Petri net with $S$ as its set of species and no transitions \cite[Lemma 11]{BM}.   Since both $\Set$ and $\Petri$ have finite colimits and $L$ preserves them, Theorem \cref{thm:SC} yields a symmetric monoidal double category $\lOpen(\Petri)$ of open Petri nets which has:
\item objects given by sets,
\item vertical 1-morphisms given by functions,
\item horizontal 1-cells as \define{open Petri nets}, which are cospans in $\Petri$ of the form:

@@

\item 2-morphisms as maps of cospans in $\Petri$ of the form:

@@

\node (F') at (5,-1) {$L(Y_2)$.};
